---
title: "Lab 00 - Hello IDS!"
author: "sophia cauter"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("alba", "tarana", "may", 
           "ada", "arshpreet"),
  github_username = c("alba2728", "taranaedwards", "username 2", 
                      "mayuco168", "username 4"), 
  colour = c("springgreen2", "steelblue1", "peachpuff1", 
             "whitesmoke", "mediumorchid3"),
  hobby = c("mathsoc netball", "napping", "reading", 
            "guitar", "art"),
  favourite_number = c(2, 3, 5, 7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows the data entered above about my teams favourite number, colour and username


### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Favourite Number", 
          y = "additional info",
          title = "Team Info")
```

the command adds labels to the diagram that is plotted

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It is likely that there would be lots of different hobbies and each one would take up a large bar on the screen while the actual hobbies would be a lot smaller. There is also no need for decimal points on the table as it is only possible for discrete data. Maybe a list with a larger scale and just lines rather than large bars so it is easier to read through the different hobbies.
